
\documentclass[a4paper,10pt]{article}
\newcommand{\AppDate}{December $|$ 2019}
\usepackage{C:/Users/thoma/OneDrive/Documents/GitHub/TemplateTex/src/cvedu}

\begin{document}
\pagestyle{plain}
\USheader

\section{Work Experience}
\begin{tabularx}{\textwidth}{cX}
2017 - 2020 & \textbf{MTT Innovation Inc.} \hfill \textbf{Vancouver, Canada} \\
& \textit{Internal \& External Venturing} | 2019 - present \\
& Joined the Executive Committee of the newly appointed CTO in the parent company, Barco NV,
as advisor on R\&D portfolio management and new acquisitions. %roadmaps and %technology
Charged with coaching R\&D globally to change corporate culture from a siloed product-driven %guide, steer
structure to technology-driven internal ventures. \\
& \\
& \textit{Sr. Research Engineer, project lead} | 2017 - 2019 \\
& Created and led 3 key projects, including: a \nth{3} Horizon computational optics innovation in additive manufacturing
with a focused team of 3 scientists, a \nth{2} Horizon foundational laser assembly technology and plant with \$5M 
in investments and a team of 15 engineers in Europe and Canada and a \nth{1} Horizon Joint Development for a 
common platform design with Sony Corporation in Japan.
%\nth{1} horizon Joint Development with Sony Research in Japan, \nth{2} foundational laser assembly technology and plant 
%with a team of 15 engineers in Europe and Canada and \$5M in investments, 2) a disruptive optical innovation
%in additive manufacturing with a focused team of 3 scientists and 3) a Joint Development with Sony Research
%in Japan.
%& Started and led 3 key projects for the newly acquired startup; 1. a new laser manufacturing technology
%foundational to the next generation products with a team of 15 scientists and \$5M in investments,
%2. a disruptive optics innovation in additive manufacturing with a focused team of 3 and 3. a Joint Development 
%with Sony Corporation in Japan.
%& Created and led 3 key projects for the company including, 1. a new foundational laser manufacturing 
%technology with a team of 12 engineers and scientists in Canada and Belgium, 2. a new optics innovation initiative
%in Additive manufacturing with a team of 3 engineers and 3. a Joint Development with a large team from 
%Sony corporation in Japan.
% optics
\\
& \\
& Awarded the IEEE Young Innovator of the Year Award in Industrial Electronics, 2019. \\
& \\
2014 - 2017 & \textbf{The University of Tokyo} \hfill \textbf{Tokyo, Japan} \\
& \textit{Research Associate, Department of Electrical Engineering} \\
& Conducted research on optimal control theory in an all-Japanese lab. Published new control algorithms 
based on high-order statistical modeling and demonstrated them in industry with %challenges %on real-world issues
a small team of researchers and partners incl. Nikon, Mori-Seiki 
and Toyota for their upcoming electrical vehicle. \\
%&Joined an all-Japanese research group on control algorithm design and industrial electronics.
%Proposed several new algorithms based on statistical modeling and collaborated with industrial research centers 
%to apply the algorithm in their machines, including Nikon in Semiconductor stages, Mori-Seiki in 
%Precision machining and Toyota Motors in their upcoming electrical vehicle.
%\\
& \\
& Awarded the Mori-Seiki Corporation President's Research Fellowship, 2015 - 2017. \\
& \\
2009 - 2020 & \textbf{Vandewiele Group} \hfill \textbf{Kortrijk, Belgium} \\
& \textit{Board Member} | 2015 - present \\
& Joined the board of the family business to guide manufacturing investments and technology acquisitions. \\
& \textit{Engineering Intern} | 2009 - 2015 \\
& Yearly summer internship, first at key textile customers in Belgium, Turkey and Russia, then at 
machinery R\&D divisions in Belgium and Sweden and finally at production sites in China and Japan. \\
& \\
\end{tabularx}

\section{Education}
\begin{tabularx}{\textwidth}{cX}
2013 - 2014 & \textbf{Catholic University of Leuven} \hfill \textbf{Leuven, Belgium} \\
\small{English} & Earned a Master of Science in Mechatronics Engineering, cum laude. \\
& \\
2012 - 2013 & \textbf{Technical University of Munich} \hfill \textbf{Munich, Germany} \\
\small{German} & Selected for a joint university program abroad with an Erasmus Scholarship for a full academic year. 
Specialized in Robotics and Automotive Manufacturing, cum laude. \\
& \\
2009 - 2012 &  \textbf{Catholic University of Leuven} \hfill \textbf{Leuven, Belgium} \\
\small{Dutch} & Earned a Bachelor of Science in Mechanical Engineering, cum fructu. \\
& \\
\end{tabularx}

\section{Extra-Curricular}
\begin{tabularx}{\textwidth}{cX}
2009 - 2012 & \textbf{Rugby, captain of the University Team} \hfill \textbf{Leuven, Belgium} \\
& Following 6yrs as a fullback for a \nth{1} division team in Brussels, I was asked to lead the university 
team. Organized bi-weekly trainings, brought in international players and changed team tactics and culture. 
Led the team to the provincial final the first year and the national final the two following years. \\
& \\
2009 - 2012 & \textbf{Scouting, Federation of Catholic Scouts} \hfill \textbf{Brussels, Belgium} \\
& Responsible for the junior section of a scouts group in a disadvantaged neighboorhood of Brussels. \\
& \\
Languages & Fluent in Dutch, English and French. Good knowledge of German and basic understanding of Japanese. \\
& \\
Personal & Avid interest in History, Paintings and Architecture. \\
\end{tabularx}

\newpage
\section{Selected Publications (Peer-Reviewed Conference \& Journal Papers)}
\begin{tabularx}{\textwidth}{cX}

\multicolumn{2}{l}{\textbf{Electric Vehicles}} \\
\multicolumn{2}{l}{in collaboration with Toyota Motor Corporation, Advanced Engineering Division} \\
& \\
	
[1] & S.~Yamada, \textbf{T.~Beauduin}, H.~Fujimoto, T.~Kanou and E.~Katsuyama ``{Active model-based 
	suppression of secondary ride for electric vehicles with in-wheel motors},''
	in \emph{IEEE Transactions on Vehicular Technology}, xx (x), 2020. 
	Impact Factor: 6.41 | Status: In Print. \\
	& \\
	
[2] & \textbf{T.~Beauduin}, S.~Yamada, H.~Fujimoto, T.~Kanou and E.~Katsuyama, ``{Control-oriented modelling 
	and experimental modal analysis of electric vehicles with geared In-Wheel motors},'' in \emph{IEEE 
	International Conference on Advanced Intelligent Mechatronics} (AIM), 2017.
	Impact Factor: 1.02 | Status: Published. \\
& \\
	
[3] & S.~Yamada, \textbf{T.~Beauduin}, H.~Fujimoto, T.~Kanou and E.~Katsuyama, ``{Model-based 
	longitudinal vibration suppression control for electric vehicles with geared in-wheel motors},'' 
	in \emph{IEEE International Conference on Advanced Intelligent Mechatronics} (AIM), 2017.
	Impact Factor: 1.02 | Status: Published. \\
& \\

\multicolumn{2}{l}{\textbf{Precision Machining}} \\
\multicolumn{2}{l}{in collaboration with Mori-Seiki Corporation, Servo Development Group} \\
& \\

[4] & \textbf{T.~Beauduin}, H.~Fujimoto, Y.~Terada and N.~Kumagai, ``{Distributed Friction Modeling and 
	Compensation for Precision Machining},'' in \emph{International Journal of Machine Tools and 
	Manufacture}, xx (x), 2020.
	Impact Factor: 6.03 | Status: Submitted. \\
& \\

[5] & \textbf{T.~Beauduin}, H.~Fujimoto and Y.~Terada, ``{Distributed and Parameter-Varying Friction 
	Compensation for Ball-Screw Feed Drive Systems},'' in \emph{IEEJ International Workshop on 
	Sensing, Actuation, Motion Control, and Optimization} (SAMCON), 2017. 
	Impact Factor: 0.56 | Status: Published. \\
& \\

[6] & \textbf{T.~Beauduin} and H.~Fujimoto, ``{Adaptive vibration suppression perfect tracking 
	control for linear time-varying systems with application to ball-screw feed drives},'' 
	in \emph{IEEE 14th International Workshop on Advanced Motion Control} (AMC), 2016. 
	Impact Factor: 0.67 | Status: Published. \\
	& \\

[7] & \textbf{T.~Beauduin}, H.~Fujimoto and Y.~Terada, ``{Control-Oriented Modeling and Parametric 
	Identification of Coupled Dynamics in Ball-Screw-Driven Systems},'' 
	in \emph{IEEJ International Workshop on Sensing, Actuation, Motion Control, and Optimization} (SAMCON), 2016. 
	Impact Factor: 0.56 | Status: Published. \\
& \\

\multicolumn{2}{l}{\textbf{Semiconductor Machinery}} \\
\multicolumn{2}{l}{in collaboration with Nikon Corporation, FDP Lithography Business Unit} \\
&\\

[8] & W.~Ohnishi, \textbf{T.~Beauduin}, and H.~Fujimoto, ``{High-precision tracking control for 
	non-minimum phase system: General framework of finite time preactuation with multirate feedforward},'' 
	in \emph{IEEE/ASME Transactions on Mechatronics}, 24 (2), 2020. 
	Impact Factor: 5.71 | Status: Submitted. \\
	& \\

[9] & W.~Ohnishi, \textbf{T.~Beauduin}, and H.~Fujimoto, ``{Preactuated Multirate Feedforward Control 
	for Independent Stable Inversion of Unstable Intrinsic and Discretization Zeros},'' 
	in \emph{IEEE/ASME Transactions on Mechatronics}, 24 (2), 2019. 
	Impact Factor: 4.99 | Status: Published. \\
	& \\

[10] & W.~Ohnishi, \textbf{T.~Beauduin}, and H.~Fujimoto, ``{Optimal State Trajectory Regeneration 
	for Nonminimum Phase Systems: No Preactuation Approach},'' in \emph{IEEE Annual Conference of 
	Industrial Electronics}, (IECON), 2018.
	Impact Factor: 1.12 | Status: Published. \\
	& \\
	
[11] & \textbf{T.~Beauduin} and H.~Fujimoto, ``{Identification of System Dynamics with Time Delay: 
	a Two-Stage Frequency Domain Approach},'' in \emph{The 20th World Congress of the 
	International Federation of Automatic Control} (IFAC), 2017.
	Impact Factor: 0.96 | Status: Published. \\
	& \\

[12] & W.~Ohnishi, \textbf{T.~Beauduin}, and H.~Fujimoto, ``{Preactuated multirate feedforward
	for a high-precision stage with continuous time unstable zeros},'' in
	\emph{The 20th World Congress of the International Federation of Automatic Control} (IFAC), 2017.
	Impact Factor: 0.96 | Status: Published. \\
	& \\

%[13] & W.~Ohnishi, \textbf{T.~Beauduin}, and H.~Fujimoto, ``{Finite Time Optimal Preactuation
%	for Non-Minimum Phase Systems Considering Control Input and Tracking Error
%	Constraints},'' in \emph{IEEE Conference on Control Technology and Applications} (CCTA), 2018.
%	Impact Factor: - | Status: Published. \\
%& \\

\end{tabularx}

% ------------------
% EXPANSION SECTIONS
% ------------------
%% 
%\section{Academic Contributions}
%\begin{tabularx}{\textwidth}{cX}
%\textsc{Mar. 2016} & T. Beauduin and H. Fujimoto, "Control-Oriented Modeling and Parametric Identification of Coupled \\
%\textsc{conference}	& Dynamics in Ball-Screw-Driven Systems" in \textit{IEEJ International Workshop on Sensing, Actuation, Motion Control and Optimization, SAMCON 2016.} \\
%
%\textsc{Apr. 2016} & T. Beauduin and H. Fujimoto, "Adaptive Vibration Suppression Perfect Tracking Control for Linear- \\
%\textsc{conference} & Time-Varying Systems applied to Ball-Screw-Driven Systems" in \textit{The 15th International Workshop on Advanced Motion Control, AMC 2016.} \\
%\textsc{Jun. 2016} & Frequency Domain System Identification for control engineers: from excitation design to \\
%\textsc{Lecture} & parametric modeling of multi-variable systems, \textit{Precision Servo Systems Committee, PSS June 2016.} \\
%& \\
%\end{tabularx}
%% SUMMARY
% full text; a few lines explaining personality

%% OBJECTIVE
% add 1 or 2 sentences with objective of application as to show
% that CV was made specifically for the application:
% ex.: Application for Project Engineering Position ...

%% CURRENT POSITION
% description of current position
% ex.: Research Student, University of Tokyo

%%	PERSONAL INTEREST
% list of personal interest: ski, rugby, runnning, ...

%%	SCHOLARSHIPS
% list of scholarships: provenance, amount, reason ...

%%	PUBLICATIONS
% list of publications: bibtex data

%%	ANNEXES
% list of documents you put in application folder
% ex.: Transcript of records, Abstract of thesis, ...

% SPORTS
% emphasis rugby carrier

% VOLUNTEERING
% emphasis social engagement
% scouts, vtk AND try to have some social activity in Todai <-> Tohoku,...
\end{document}
